---
title: "p8105_hw6_yf2563"
author: "Yatong Feng"
date: "12/7/2020"
output: github_document
---

```{r, message=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  message = F,
  warning = F
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

The Washington Post has gathered data on homicides in 50 large U.S. cities.

- Create a city_state variable (e.g. “Baltimore, MD”)
- binary variable indicating whether the homicide is solved. 
- Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. 
- omit Tulsa, AL – this is a data entry mistake. 
- For this problem, limit your analysis those for whom victim_race is white or black. 
- Be sure that victim_age is numeric.

```{r, message=FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)

head(homicide_df)
```

For the city of Baltimore, MD:

- use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. 
- Save the output of glm as an R object; 
- apply the broom::tidy to this object; 
- obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```
